Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election 

### 2024-04-13 paper/paper(1).qmd
Add files via upload

```{r setup, include=FALSE, message=FALSE}
## Import necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(here)
library(readr)
library(knitr)
library(kableExtra)
library(rstanarm)
library(arrow)
library(tidybayes)
```

@@

# Model

@@

## Model Set-up

We define our Bayesian logistic regression model for the probability of an individual voting for the Liberal/Conservative party as follows:

@@

Table2: Summary the residuals for Conservative Party:

```{r echo=FALSE, warning=FALSE}
liberal_residuals <- posterior_predict(liberal_model) - cleaned_survey_data$vote_liberal

conservative_residuals <- posterior_predict(conservative_model) - cleaned_survey_data$vote_conservative

@@

print(table_summary)
```

@@

```{r fig-liberal-model, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Liberal Model"}
library(readr)
library(bayesplot)
library(here)

>>>>

```{r setup, include=FALSE, message=FALSE}
## Import necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(here)
library(readr)
library(knitr)
library(kableExtra)
library(rstanarm)
library(arrow)
library(tidybayes)
library(bayesplot)
```

@@

# Model
We utilized the rstanarm package for constructing the generalized linear model[@R-rstanarm], the rstanarm package serves as a user-friendly interface in R for fitting Bayesian regression models using the Stan probabilistic programming language.
It enables users to effortlessly construct various types of regression models, including linear, logistic, and Poisson regression, while leveraging the power of Bayesian methods for inference.
By seamlessly integrating with Stan, rstanarm provides efficient algorithms for model fitting and accurate estimates of uncertainty.
Additionally, the package offers diagnostic tools for assessing model convergence and sensitivity to prior specifications, making it an invaluable resource for Bayesian data analysis in R.

@@

## Model Set-up
We define our Bayesian logistic regression model for the probability of an individual voting for the Liberal/Conservative party as follows:

@@

Table2: Summary the residuals for Conservative Party:
```{r echo=FALSE, warning=FALSE}

liberal_residuals <- posterior_predict(liberal_model) - cleaned_survey_data$vote_liberal
conservative_residuals <- posterior_predict(conservative_model) - cleaned_survey_data$vote_conservative

@@

# Create a table of the data
kable(table_summary, caption = "Summary of Residuals by Party")

@@

```{r fig-liberal-model, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Liberal Model"}
